Forecasting the 2024 U.S. Presidential Election

### 2024-11-04 paper/paper.qmd
Updated the Pollster Appendix
Updated the Pollster Appendix

The Marquette Law School Poll employs a rigorous methodology to survey adults in the US on national issues, incorporating probability-based sampling that combines Address-Based Sampling (ABS) and Stratified Random Sampling [@citemarquette]. This approach, including online and offline respondents, ensures broad representativeness. The SSRS Polling Panel supports participant recruitment, and weighting adjustments enhance result accuracy.

@@

The population for the poll includes adults aged 18 and over across all 50 states and the District of Columbia. The sampling frame was constructed through ABS, leveraging the US Postal Service's Computerized Delivery Sequence (CDS), a comprehensive, regularly updated list of residential addresses. The primary source for participants is the SSRS Opinion Panel, which includes both ABS and telephone survey data to capture hard-to-reach demographics, like non-internet users. The survey ultimately included 1,005 adults, including registered and likely voters, with weighted samples to ensure proportional representation [@citemarquette].

@@

Participants were recruited via the SSRS Omnibus Panel, a probability panel formed from ABS and telephone survey data. This dual approach ensured that both internet and non-internet users were included, minimizing online-only bias. Stratified by demographics (age, gender, race, education, region, and partisan affiliation), this process produced a balanced representation across groups. Selected participants received an email invitation with a unique link to the survey. Non-responders received up to two reminder emails, and those who opted for text notifications also received reminders. Participants received an e-gift card incentive upon survey completion [@citemarquette].

@@

The Marquette Law School Poll combines ABS and stratified random sampling. The ABS covers all residential addresses using USPS delivery sequences, ensuring broad geographic reach. To include hard-to-reach demographics, SSRS supplements ABS data with telephone survey responses. Stratified sampling by key demographics (age, gender, race, education, region, and political party) ensures representation across major groups [@citemarquette]. This probability-based sampling minimizes bias but requires significant resources. Stratification and weighting to represent specific populations add to survey complexity and cost.

@@

To address non-response and improve representativeness, SSRS applies weighting adjustments based on demographic variables such as age, gender, race, education, region, and internet use [@citemarquette]. This process aligns sample characteristics with adult population parameters, reducing bias from demographic differences in response rates.

@@

The questionnaire is well-designed, with a collaborative approach that reduces respondent burden and improves comprehension. A thoughtfully structured skip pattern enhances flow and minimizes dropout rates. The probability-based sampling, combined with extensive weighting and stratification, enables a representative sample of adults. However, heavy reliance on web-based responses may introduce internet bias, potentially underrepresenting non-internet households. Additionally, the questionnaire’s complexity may increase participant fatigue, affecting response completeness. The response rate of approximately 47.4% also indicates some level of attrition in the sample [@citemarquette].

>>>>

The Marquette Law School Poll utilizes a rigorous probability-based methodology to conduct a national question survey of adults across the United States. This method combines address-based sampling (ABS), which uses the U.S. Postal Service's Computerized Delivery Sequence (CDS), and stratified random sampling, which covers virtually all residential addresses and is able to reach the offline population, thereby reducing the bias associated with surveys conducted solely via the Internet [@citemarquette]. The stratified random sampling method divides the population into subgroups (e.g., age, gender, education), to make sure that each subgroup is proportionately represented in the sample. This structure improves representativeness and accuracy, thereby supporting valid inferences about the total U.S. adult population.

@@

The population surveyed by the Marquette Law School Poll includes all U.S. adults aged 18 and older, living in the 50 states and D.C. The sampling frame was developed using Address-Based Sampling (ABS) by using the U.S. Postal Service’s Computerized Delivery Sequence (CDS) file—a regularly updated, near-complete listing of all residential addresses in the U.S., excluding business addresses. This frame can cover almost every U.S. household, including non-internet and traditionally hard-to-reach areas [@citemarquette].

The sample itself was drawn from the SSRS Opinion Panel, a probability-based panel that combines participants from ABS and a bilingual telephone survey conducted through the SSRS Omnibus. This dual recruitment strategy, which includes participants from both internet and non-internet households, improves demographic inclusivity. To achieve accurate representation, the survey sampled 1,005 adults, including registered and likely voters, and applied post-stratification weighting to adjust for demographic imbalances. This weighting aligns the sample with key population parameters, ensuring that the poll’s findings are as representative as possible of the broader adult population.

@@

Marquette Law School Poll using the SSRS Opinion Panel for the recruitment, a probability-based panel integrating Address-Based Sampling (ABS) and telephone survey data from the SSRS Omnibus, a nationally representative bilingual survey platform. This dual recruitment approach ensures that both internet and non-internet users are included, addressing the online-only bias often seen in web-based surveys and thereby enhancing sample inclusivity [@citemarquette].

The Marquette Law School Poll uses stratified sampling to obtain a balanced and representative sample by differentiating participants based on key demographic variables such as age, gender, race, education, region, and political affiliation. The poll then ensures proportional representation of key demographic groups, which reduces the risk of sampling bias and increases the generalizability of the results.

Selected participants received a unique survey link through email invitations. Non-responders were sent up to two reminder emails, and, for those who opted in, a text notification reminder. To encourage completion and maintain high response rates, participants were offered an e-gift card as an incentive. This use of reminders and incentives is critical in minimizing non-response bias, thereby strengthening the reliability of the poll’s findings.

@@

The Marquette Law School Poll uses both sampling probability sampling methods, address-based sampling (ABS) and stratified random sampling, this can increase representativeness and inclusiveness. ABS uses the U.S. Postal Service's Computerized Delivery Sequence (CDS), which covers nearly all residential addresses in the U.S., including homes with no Internet access. This approach is critical to minimizing the coverage bias associated with web-only surveys [@citemarquette].

The poll also applies stratified random sampling to ensure that key demographic groups—such as age, gender, race, education, region, and political affiliation—are proportionally represented within the sample. Samples are taken from each subgroup once the population is divided into subgroups using stratified sampling. Consequently, sampling error is reduced and the sample findings accurately represent the views of each subgroup.

While this approach increases the reliability and representativeness of the findings, it also demands significant resources. ABS requires comprehensive address data and ongoing maintenance, while stratification and post-stratification weighting add complexity to both survey design and data processing. These resource-intensive processes make ABS and stratified random sampling more costly than simpler sampling methods but are justified by the improved accuracy and generalizability of the poll’s results.

@@

The Marquette Law School Poll applies weighting adjustments across demographic factors, including age, gender, race, education, region, and internet access, aligning the sample’s characteristics with those of the broader adult population [@citemarquette]. This can represent the under-represented groups more accurately and increase the weight of these respondents. This process enhances the survey’s representativeness, ensuring findings reflect the national population reliably despite disparities in response rates.

@@

The Marquette Law School Poll is designed to boost respondent engagement and minimize survey fatigue. Using skip patterns that adapt questions based on previous answers, the survey reduces cognitive load, streamlines flow and lowers dropout rates by customizing the survey experience [@citemarquette]. This probability-based approach, supplemented by comprehensive weighting and stratification, further makes sure that the results accurately represent the U.S. adult population, with clear and straightforward questions that enhance accessibility across demographic groups.

However, despite ABS and telephone recruitment efforts, the reliance on web-based responses can cause some internet bias possibly underrepresenting households with no internet access. Additionally, the survey’s length and complexity could add to respondent fatigue, potentially impacting response quality as participants progress. The response rate of approximately 47.4% reflects moderate attrition, typical in public opinion research, highlighting the necessity of post-stratification adjustments to address any demographic imbalances from non-response.
